### 2019-03-19 paper.tex
n1 grafx added

\usepackage{amsmath}
\usepackage{ptolemaicastronomy}
\usepackage[backend=biber,authordate,
ibidtracker=context,natbib,doi=false,isbn=false,url=false]{biblatex-chicago}

@@

@@

By the success postulate, we cannot drop \(p\). Since \(b \rightarrow f\) can be
assumed to be analytic, we won't drop that, either. Dropping either $b \rightarrow
f$ or $p \rightarrow \neg f$ leads to a revision satisfying postulates $K^*1 -
K^*8$. To decide between the two options in our formalism, we need additional
structure. There are a host of different such structures developed, prominently
a procedure called \emph{partial meet contraction}
\parencite[p.~80]{gaerdenfors88_knowl} and a notion called
\emph{epistemic entrenchment} \parencite[p.~86]{gaerdenfors88_knowl}. Both
are relational structures designed to prescribe a choice. Partial meet
contraction introduces a relation on maximal subsets of $K$ which don't  
imply $p$, while epistemic entrenchment orders sentences in K. To facilitate an
intuitive notion, I present a third `semantics' based on a sphere system by
\textcite{grove88_two_model_theor_chang} (also cf. \textcite[p.~83]{gaerdenfors88_knowl})

@@

\begin{figure}[ht]
    \centering
    \label{fig:spheres1}
    \begin{tikzpicture}[scale=1]
        % wider layers, pointier propositions
        \tikzset{layerwidth=1,innerfactor=0,
          proposition/.style={smooth,tension=1}}
        % fill the areas between three props and their innermost spheres
        % \sphereintersect{3}{\propositionplot{30}{3.3}{30}{4}}
        \sphereintersect{2}{\propositionplot{30}{2.3}{45}{4}}
        % \sphereintersect{1}{\propositionplot{30}{1.3}{60}{4}} draw the sphere
        % system
        \spheresystem[solid]{3}
        % draw the propositions \draw \propositionplot{30}{3.3}{30}{4};
        \draw \propositionplot{30}{2.3}{45}{4};
        % \draw \propositionplot{30}{1.3}{60}{4}; draw \psi (coordinates figured
        % out by trial and error) \draw plot[smooth,tension=1.2] coordinates
        % {(-1.5,3) (1.2,-1) (.8,2.3) (2.8,.7) (3,4)}; draw and label the center
        % world, spheres, and propositions
        % \filldraw circle[radius=.05];
        \node at (0,0) {$[K]$};

        \spherepos[fill]{30}{2.2}{circle[radius=.1]}
        \spherepos[fill]{22}{2.3}{node {$i$}}
        % \spherepos{-70}{1.8}{node {$S_1$}}
        \spherepos{-70}{2.8}{node{$S_1$}}
        \spherepos{-70}{3.8}{node {$S_2$}}
        % \spherepos{4}{4.3}{node {$\phi_1$} node at +(0,.5) {$\phi_2$} node at
        %   +(0,1) {$\phi_3$}}
        \spherepos{4}{4.3}{node at +(0,.5) {$[p]$}}
        % \spherepos{80}{4}{node {$\psi$}}
    \end{tikzpicture}

    \caption{Belief set $K$ in a system of spheres.}
\end{figure}

How does this help with choosing between dropping $b \rightarrow
f$ or $p \rightarrow \neg f$? Depending on the agent's sphere system, either $i
\models p \land b \land f$ or $i \models p \land b \land \neg f$. Intuitively,
either the agent finds it more plausible that penguins fly or they
don't.\footnote{Note to self: what if $i_1 \models p \land f$ and $\i_2 \models
  p \land \neg f$, $i_1,i_2 \in K^*p$?} With the help of this additional
structure, then, we can model the example as we please.

\subsection{Non-monotonic Logic: Preferential Semantics}
\section{Erik Olsson's Critique}
\section{Discussion and Conclusion}
\nocite{rott01_chang_choic_infer,olsson03_belief_revis_ration_choic_unity_reason,gaerdenfors88_knowl,gaerdenfors94_nonmon_infer_based_expec,alchourron85_logic_theor_chang,makinson91_relat,sen93_inter_consis_choic,kraus90_nonmon_reason_prefer_model_cumul_logic,hansson17_logic_belief_revis,
  ortner11_mechan_induc,brewka97_nonmon} \printbibliography
\end{document}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{ptolemaicastronomy}
\usepackage{ebproof/ebproof}
\usepackage[backend=biber,authordate,
ibidtracker=context,natbib,doi=false,isbn=false,url=false]{biblatex-chicago}

@@

\newcommand{\nc}{\,\mid\!\sim\,}

@@

By the success postulate, we cannot drop \(p\). Since \(b \rightarrow f\) can be
assumed to be analytic, we won't drop that, either. Dropping either $b \rightarrow
f$ or $p \rightarrow \neg f$ leads to a revision satisfying postulates $K^*1 -
K^*8$. To decide between the two options in our formalism, we need additional
structure. There are a host of different such structures developed, prominently
\emph{partial meet contraction}
\parencite[p.~80]{gaerdenfors88_knowl} and 
\emph{epistemic entrenchment} \parencite[p.~86]{gaerdenfors88_knowl}. Both
are relational structures designed to prescribe a choice. Partial meet
contraction introduces a relation on maximal subsets of $K$ which don't  
imply $p$, while epistemic entrenchment orders sentences in K. To facilitate an
intuitive notion, I present a third `semantics' based on a sphere system by
\textcite{grove88_two_model_theor_chang} (also cf. \textcite[p.~83]{gaerdenfors88_knowl})

@@

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[scale=1]
        % wider layers, pointier propositions
        \tikzset{layerwidth=1,innerfactor=0,
          proposition/.style={smooth,tension=1}}
        % fill the areas between three props and their innermost spheres
        % \sphereintersect{3}{\propositionplot{30}{3.3}{30}{4}}
        \sphereintersect{2}{\propositionplot{30}{2.3}{45}{4}}
        % \sphereintersect{1}{\propositionplot{30}{1.3}{60}{4}} draw the sphere
        % system
        \spheresystem[solid]{3}
        % draw the propositions \draw \propositionplot{30}{3.3}{30}{4};
        \draw \propositionplot{30}{2.3}{45}{4};
        % \draw \propositionplot{30}{1.3}{60}{4}; draw \psi (coordinates figured
        % out by trial and error) \draw plot[smooth,tension=1.2] coordinates
        % {(-1.5,3) (1.2,-1) (.8,2.3) (2.8,.7) (3,4)}; draw and label the center
        % world, spheres, and propositions
        % \filldraw circle[radius=.05];
        \node at (0,0) {$[K]$};
        \spherepos[fill]{30}{1}{circle[radius=.05]}
        \spherepos[fill]{120}{1}{circle[radius=.05]}
        \spherepos[fill]{270}{1}{circle[radius=.05]}
        \spherepos[fill]{30}{2.2}{circle[radius=.05]}
        \spherepos[fill]{45}{3.2}{circle[radius=.05]}
        \spherepos[fill]{22}{2.3}{node {$i$}}
        % \spherepos{-70}{1.8}{node {$S_1$}}
        \spherepos{-70}{2.8}{node{$S_1$}}
        \spherepos{-70}{3.8}{node {$S_2$}}
        % \spherepos{4}{4.3}{node {$\phi_1$} node at +(0,.5) {$\phi_2$} node at
        %   +(0,1) {$\phi_3$}}
        \spherepos{4}{4.3}{node at +(0,.5) {$[p]$}}
        % \spherepos{80}{4}{node {$\psi$}}
    \end{tikzpicture}

    \caption{Belief set $K$ in a system of spheres.}

    \label{fig:spheres1}
\end{figure}

How does this help with choosing between dropping $b \rightarrow
f$ or $p \rightarrow \neg f$? Depending on the agent's sphere system, either $i
\models p \land b \land f$ or $i \models p \land b \land \neg f$. Intuitively,
either the agent finds it more plausible that penguins fly or they
don't.\footnote{Note to self: what if $i_1 \models p \land f$ and $\i_2 \models
  p \land \neg f$, $i_1,i_2 \in K^*p$?} With the help of this additional
structure, then, we can uniquely define a revision.

Grove's sphere systems are provably `sound and complete' for revision functions
satisfying $(K^*1)-(K^*8)$, in a sense made precise by \textcite[][p.~84-85]{gaerdenfors88_knowl}.

\subsection{Non-monotonic Logic}

Non-monotonic logics define an conditional or a consequence relation that does
not satisfy monotonicity, i.e. additional evidence can demand a retraction of
previously drawn inference. Formally, the following inference is not valid for $\nc$. 
\begin{center}
    \begin{prooftree}
        \hypo{ \alpha \nc \beta } \infer1[(Mon)]{ \alpha \land \gamma \nc \beta}
    \end{prooftree}
\end{center}
I focus here on a type of non-monotonic logic called
\emph{preferential logic} developed by
\textcite{kraus90_nonmon_reason_prefer_model_cumul_logic}. KLM discuss a host of
conditions that the consequence relation can instead satisfy, and develop semantics for
salient sets of these conditions. For example, they introduce a weaker notion called 
cautious monotonicity:
\begin{center}
    \begin{prooftree}
        \hypo{ \alpha \nc \beta } \hypo{\alpha \nc \gamma} \infer2[(CMon)]{
          \alpha \land \beta \nc \gamma}
    \end{prooftree}
\end{center}
Important resulting logics are \textbf{C} (for cumulativity), \textbf{P} (for preferential), and \textbf{R}
(for rational), in increasing order of strength.

Hans Rott shows that there is a close relation between the conditions
and the AGM postulates for revision
\parencite[p.~118,137]{rott01_chang_choic_infer}. Via the Gärdenfors-Makinson
identity, we can interdefine the two theoretical approaches:
\[ \beta \in K^*\alpha \text{ iff } \alpha \nc \beta \] for sentences
$\alpha,\beta \in \mathcal{L}$ and belief set $K$. Whether a sentence $\beta$
is included in the revision of $K$ by a sentence $\alpha$ can be seen as
validating a non-monotonic inference from $\alpha$ to $\beta$.

To spell this out a bit more, let's have a intuitive, brief look at a
(non-rigorous, simplified, finite)
version of the semantics for system \textbf{R} that \textcite{lehmann1992does}
define. A ranked model assigns each world $w \in W$ a rank $rk: W \rightarrow \mathbb{N}$
such that a relation $\prec$ on $W$ can be defined for all $w_1,w_2 \in W$:
\[
 w_1 \prec w_2 :\iff rk(w_1) < rk(w_2).
\]

Such a model validates a non-monotonic conditional $\alpha \Rightarrow \beta$ if
and only if the $\prec$-minimal $\alpha$-worlds are also $\beta$-worlds (compare
Figure \ref{fig:rank1} and \textcite[][p.~748]{ortner11_mechan_induc}).

\begin{figure}[ht]
    \centering
\begin{tikzpicture}
% \draw[help lines, thick] (0,0) grid (4,4);
\begin{scope}
\clip(0,0)rectangle(2,2);
\draw[fill,lightgray] (1.,3.5) circle [x radius=0.75, y radius=2.25];
\end{scope}\draw[rounded corners] (0, 0.1) rectangle (3, 1);
\draw[rounded corners] (0, 1.1) rectangle (3, 2);
\draw[rounded corners] (0, 2.1) rectangle (3, 3);

\draw[fill] (0.5,0.55) circle (0.05);
\draw[fill] (1.5,0.55) circle (0.05);
\draw[fill] (2.5,0.55) circle (0.05);
\draw[fill] (1,1.55) circle (0.05);
% \draw[fill] (2,1.55) circle (0.05);
\draw[fill] (0.5,2.55) circle (0.05);
\draw[fill] (1.5,2.55) circle (0.05);
% \draw[fill] (2.5,2.55) circle (0.05);

\draw (0.25,3.5) arc[start angle=180,end angle=360, x radius=0.75, y radius=2.25] node[left] {$\alpha$};

\end{tikzpicture}
\caption{A ranked model. The $\prec$-minimal worlds satisfying $\alpha$ are shaded.}
\label{fig:rank1}
\end{figure}

Now the similarity to the sphere system described in the preceding section is
not just superficial; we can in fact transform the ranked model into a sphere
system by setting $[K]$ to the $\prec$-minimal worlds, $S_1$ to the union of
$[K]$ and the $\prec$-minimal worlds of $W \ [K]$ and so forth. The semantics of
revision by $p$ are then very similar to validating a non-monotonic conditional
$\alpha \rightarrow \beta$. Note that we get this very neat correspondence of
the semantics not in all cases. In particular, the Grove sphere system requires
$(K^*1)-(K^*8)$, and ranked models are adequate for the strong logic \textbf{R}.

\subsection{Rational Choice}

\section{Erik Olsson's Critique}
\section{Discussion and Conclusion}
\nocite{rott01_chang_choic_infer,olsson03_belief_revis_ration_choic_unity_reason,gaerdenfors88_knowl,gaerdenfors94_nonmon_infer_based_expec,alchourron85_logic_theor_chang,makinson91_relat,sen93_inter_consis_choic,kraus90_nonmon_reason_prefer_model_cumul_logic,hansson17_logic_belief_revis,
  ortner11_mechan_induc,brewka97_nonmon} \printbibliography
\end{document}
